Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
Continue work on eval section

For some applications, the absolute best accuracy is not something desirable if
it implies having enormous models. This observation motivates our methodology:
for a given target accuracy that you want your model to achieve, we pick the
smallest that satisfy the constraint. For both \textit{ShrinkNets} and
\textit{Static Networks} we measure multiple metrics and compute the ratio
between the two. The metrics are interested in are: the final model size (in
number of parameters) and inference speed on CPU and GPU for small batch sizes
($1$ input) and large batch sizes (depend on the dataset and hardware).

@@

\textbf{TODO: Interpret the results}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{neuron_removal}
\vspace*{-5mm}
\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$. First column is the difference in the final loss in function of the removal factor. We plot theoretical baseline as a reference. Right column is a proxy of the total cost for training the model (i.e. the sum of input neurons at each epoch). Each row is a dataset/$\lambda$ combination. From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{COVER}
\end{center}
\vspace*{-4mm}
\end{figure}

\section{Speeding up training with pruning}

>>>>

For some applications, the absolute best accuracy is not something desirable if
it implies having enormous models. This observation motivates our methodology:
for a given target accuracy that you want your model to achieve, we pick the
smallest that satisfy the constraint. For both \textit{ShrinkNets} and
\textit{Static Networks} we measure multiple metrics and compute the ratio
between the two. The metrics are interested in are: the final model size (in
number of parameters) and inference speed on CPU and GPU for small batch sizes
($1$ input) and large batch sizes (depend on the dataset and hardware). Results
are shown on \cref{figure_CIFAR10} and \cref{figure_COVER} after the
distribution of sizes and accuracy. We limit our plot to the ($80-100\%$
accuracy range because we consider that models with lower accuracy have less
practical use).

Regarding size, the key observation we can make is that size improvenets are
significant for

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{neuron_removal}
\vspace*{-5mm}
\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$. First column is the difference in the final loss in function of the removal factor. We plot theoretical baseline as a reference. Right column is a proxy of the total cost for training the model (i.e. the sum of input neurons at each epoch). Each row is a dataset/$\lambda$ combination. From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset}
\end{center}
\vspace*{-4mm}
\end{figure}

\section{Architectures obtained after convergence}

We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
to make sense both in term of size and performance. And for a given accuracy the
size needed is significantly smaller than when we use the classic heursitc we
commonly use to size convolutional neural networks. It might be an indication
that this strategy is suboptimal and might need to be adjusted. During our
experimentations on simpler datasets like \texttt{MNIST} and
\texttt{FashionMNIST} we observed that even if they have the same number of
classes, input features, and output distribution. For a fixed $\lambda$
\textit{ShrinkNets} converged to considerably bigger networks in the case of
\texttt{FashionMNIST}.
take a look closer to the architectures \textit{ShrinkNets} converge to
